Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-03-16 Paper/paper.tex
Updated readme with link and including link to github in paper
Update

\begin{itemize}
    \item The assumptions as to the strategy space of our players is restrictive: a single threshold policy might not be optimal (although it is present in various pieces of literature on optimal control of queueing systems: \cite{knight2012comparisons, naor1969regulation});
    \item This model only assumes the presence of two players however in reality the system has a variety of stakeholders. Multi player systems could be worth considering;
    \item The restriction to pure strategies is influenced by discussions with ABHB and also does not detract from the results presented thanks to the Theorem and Lemma of Section \ref{queueingandgamemodels}.  However, allowing for mixed strategies could also be of interest.
\end{itemize}

@@

The code used in this work was written in Python and can be found here: \url{drvinceknight/measuring...}.
The graphics for this paper were obtained using \cite{Hunter:2007, sage} a worksheet with the data and code used for the plots can be found here: \url{https://sage.maths.cf.ac.uk/home/pub/122/}.

>>>>

\begin{itemize}
    \item The assumptions as to the strategy space of our players is restrictive: a single threshold policy might not be optimal (although it is present in various pieces of literature on optimal control of queueing systems: \cite{naor1969regulation, shone2013comparisons});
    \item This model only assumes the presence of two players however in reality the system has a variety of stakeholders. Multi player systems could be worth considering;
    \item The restriction to pure strategies is influenced by discussions with ABHB and also does not detract from the results presented thanks to the Theorem and Lemma of Section \ref{queueingandgamemodels}.  However, allowing for mixed strategies could also be of interest.
\end{itemize}

@@

The code used in this work can be found here: \url{https://github.com/drvinceknight/Measuring_the_price_of_anarchy_in_ccu_interactions}.
The graphics for this paper were obtained using \cite{Hunter:2007, sage} a worksheet with the data and code used for the plots can be found here: \url{https://sage.maths.cf.ac.uk/home/pub/122/}.
